### 2016-01-13 paper-Ro_Man-2016.tex
first commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
Influence of child-robot spacial arrangement in a learning by teaching task}

\author{A1$^{1}$ and A2$^{2}$% <-this % stops a space
\thanks{}% <-this % stops a space
\thanks{$^{1}$A1 is with Faculty of A1,
        University of A1, country
        {\tt\small A1 email}}%
\thanks{$^{2}$A2 is with Faculty of A2,
        University of A2, country
        {\tt\small A2 email}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper we present a study in which we test the influence of child-robot spatial arrangement on child's focus of attention, child's perception of robot's performance in the CoWriter learning by teaching activity.
In this activity the child teaches a Nao obot how to handwrite. 
In our study, we explore two spatial condition from Kendon's F formation, the side-by-side and the face-t-face formations.

We have 3 conditions following Kendon's F formation: 
\begin{itemize}
\item side by side
\item face to face
\item in L shape
\end{itemize}

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
Cowriter

In this activity the child plays the role of a teacher.

\section{RELATED WORKS}
Proxemics

Role attribution

Kendon F Formation in HRI
\cite{huttenrauch2006investigating}

We propose to study the impact of spatial arrangement on engagement of children a handwriting task
\section{APPROACH}

within subject, 2 robots in front of the child who has to teach to the two robots

Hypothesis
\begin{itemize}
\item Child feels more in a teacher student relationship when facing the robot
\item child feels more in a peer to peer when the robot is in L or side by side 
\item how does it influence the engagement -> with-me-ness
\item  does the child looks more at the experimenter when the robot is badly behaving
\item how does the child rates the robots performances according to  the arrangement
\end{itemize}

\section{METHOD}

\section{RESULTS}

\subsection{Seriousness}

\subsection{With-me-ness}
Present it as a measure of synchrony,

Get time when robot looking where and see if similar pattern with child

\subsection{Performances}

\subsection{Questionnaire on likeability and Interrelationship}

\section{CONCLUSIONS}

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{ACKNOWLEDGMENT}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{abbrv}
\bibliography{fformation_cowriter}

\end{document}

### 2016-02-02 paper-Ro_Man-2016.tex
add outline
advances on intro and measures

@@
 %\usepackage{amssymb}  % assumes amsmath package installed
+
+\usepackage[pdftex]{graphicx}
+%\graphicspath{}
 
@@
 \item face to face
-\item in L shape
+%\item in L shape
 \end{itemize}
@@
 \section{INTRODUCTION}
-Cowriter
+Interaction settings are crucial for
+
+The Co-Writer projects aims to help children with difficulties in handwriting \cite{hood2015when}. 
+It is based on the idea of learning by teaching. 
+By teaching a Nao robot how to write, children learn and improve their handwriting. 
+The activity also plays with the protégé effect that make children more motivated in practising for the robot than for themselves.
+
+Previous studies in the Co-Writer project helped us to develop a system that generates handwriting for the robot based on demonstrations from the child\cite{hood2015when}. 
+Case studies presented in \cite{jacq2016building} showed that children were able to stay engaged in long term interaction with repeated session within the Co-Writer activity in real pedagogical/therapeutic contexts.
+These works proved to have a positive effect on extrinsic motivation of children when practising their handwriting thanks to the protégé effect.
 
@@
 
-\section{RELATED WORKS}
 Proxemics
@@
 We propose to study the impact of spatial arrangement on engagement of children a handwriting task
+
+\section{RELATED WORKS}
+
+Perspective taking: speaker with partners tend yo use more egocentric perspective rather than solo speakers \cite{Schober}
+
+Handwriting linked to spatial-sequential ability of the child. 
+This is also linked to perspective taking ability of the child.
+
+The 3 spatial perspective taking rules state that :
+\begin{enumerate}
+\item any object will present the same visual appearance to the self and to another person if the two observer view from the same point of view.
+\item An object with different sides will be seen different if the viewers are form different side views
+\item An object homogeneous in all sides will be the same from different view. 
+\end{enumerate}
+
+\cite{Newcombe1992} shows that children around the age of 5 are able to complete perspective taking tasks and to imagine what others point of you might look like.
+
 \section{APPROACH}
+In this study, each child saw interacted with the robot in the two conditions in a random order.
 
-within subject, 2 robots in front of the child who has to teach to the two robots
+within subjects Repeated measures
 
@@
 \section{METHOD}
+25
+
+Number of child
+Expe settings
+Condition within subject but with 
+\begin{figure}
+\centering
+\includegraphics[width=0.7\linewidth]{./figures/s2s_photo.jpg}
+\caption[Side by SIde Condition]{}
+\caption{}
+\label{fig:s2s_photo}
+\end{figure}
 
@@
 
-\subsection{Seriousness}
+\subsection{Reward Mechanism}
+The table interface on which the child and the robot practice their handwriting contains also two buttons that allow the child to give positive (green thumb-up) or negative (red thumb-down) feeback to the robot's handwriting.
+
+We noticed that children were expetcing the robot to react. 
+Now that the usage of these buttons have been proven, we will consider for futur experimemnt to allow the robot to react. 
+For instance, if the child gives a positive feedback when the robot is actually improving, the robot should display a positive emotion.
+If he is given a positive feedback but doesnt not actually make any progree, he might express doubt to force the child to be more exigeant.
 
 \subsection{With-me-ness}
+\cite{lemaignan2016realtime}
 Present it as a measure of synchrony,
@@
 
-\subsection{Questionnaire on likeability and Interrelationship}
+%\subsection{Questionnaire on likeability and Interrelationship}
 
@@
 
+ref all cowriter paper + paper of sharma sur withmeness
+
 \bibliographystyle{abbrv}

### 2016-02-04 paper-Ro_Man-2016.tex
advances on descripton of measures and add photos

@@
 \usepackage[pdftex]{graphicx}
+
 %\graphicspath{}
@@
 In this paper we present a study in which we test the influence of child-robot spatial arrangement on child's focus of attention, child's perception of robot's performance in the CoWriter learning by teaching activity.
-In this activity the child teaches a Nao obot how to handwrite. 
+In this activity the child teaches a Nao robot how to handwrite. 
 In our study, we explore two spatial condition from Kendon's F formation, the side-by-side and the face-t-face formations.
 
-We have 3 conditions following Kendon's F formation: 
+We have 2 conditions following Kendon's F formation: 
 \begin{itemize}
@@
 
+Robots to enhance childhood education
+
 The Co-Writer projects aims to help children with difficulties in handwriting \cite{hood2015when}. 
@@
 
-In this activity the child plays the role of a teacher.
+\cite{Matsuzoe2012} had a similar approach than learning by teaching with their Care Receiving Robot that was being taken cared off and taugh by a child with physical interaction.
 
-Proxemics
+Proxemics : explain how spatial arrangement could influence the interaction
 
@@
 
-Kendon F Formation in HRI
+Kendon F Formation in HRI: explain how spatial arrangement had influences in the past
+
+Spatial arrangement is also a social signal that tells about the relationship between the persons.
+
 \cite{huttenrauch2006investigating}
@@
 Condition within subject but with 
-\begin{figure}
+\begin{figure}[t!]
     \centering
-\includegraphics[width=0.7\linewidth]{./figures/s2s_photo.jpg}
-\caption[Side by SIde Condition]{}
-\caption{}
-\label{fig:s2s_photo}
+        \includegraphics[height=1.2in]{./figures/f2f_photo.png}
+        \caption{Face to face spatial formation}
+   ~
+        \includegraphics[height=1.2in]{./figures/s2s_photo2.jpg}
+        \caption{Side by Side spatial formation}
 \end{figure}
 
-\section{RESULTS}
+\subsection{Reward Mechanism}
+The table interface on which the child and the robot practice their handwriting contains also two buttons that allow the child to give positive (green thumb-up) or negative (red thumb-down) feedback to the robot's handwriting.
 
-\subsection{Reward Mechanism}
-The table interface on which the child and the robot practice their handwriting contains also two buttons that allow the child to give positive (green thumb-up) or negative (red thumb-down) feeback to the robot's handwriting.
-
-We noticed that children were expetcing the robot to react. 
-Now that the usage of these buttons have been proven, we will consider for futur experimemnt to allow the robot to react. 
+We noticed that children were expecting the robot to react. 
+Now that the usage of these buttons have been proven, we will consider for future experiment to allow the robot to react. 
 For instance, if the child gives a positive feedback when the robot is actually improving, the robot should display a positive emotion.
-If he is given a positive feedback but doesnt not actually make any progree, he might express doubt to force the child to be more exigeant.
+If he is given a positive feedback but doesn’t not actually make any progress, he might express doubt to force the child to be more exigent.
 
 \subsection{With-me-ness}
-\cite{lemaignan2016realtime}
+The with-me-ness measure applied in HRI in \cite{lemaignan2016realtime}, helps to set specific targets during each state of the interaction and to determine rather the user is looking at one of these targets or not.
+The algorithm is based on the d-lib library that helps to estimate the head pose of the user using a video from webcam device for instance.
+
+This measure allow us to see if the child is engage in the interaction and is looking at the tablet or the robot's head when he/she should.
+
+For this experiment, the targets where: "the observer"(a teacher or a teacher assistant), "the selection tablet"(the tablet used to pick a word),
+
 Present it as a measure of synchrony,
@@
 
-%\subsection{Questionnaire on likeability and Interrelationship}
+\section{RESULTS}
+
+\subsection{Reward Mechanism}
+
+\subsection{With-me-ness}
+
+\subsection{Performances}
 
@@
 \section*{ACKNOWLEDGMENT}
+This research was partially supported by the Funda\c{c}\~{a}o para a Ci\^{e}ncia
+e a Tecnologia (FCT) with reference UID/CEC/ 50021/2013, and by the Swiss
+National Science Foundation through the National Centre of Competence in
+Research Robotics.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-ref all cowriter paper + paper of sharma sur withmeness
 

### 2016-05-23 paper-Ro_Man-2016.tex
structured method
adding plots in the figure subfolder
update figures

--- 2016-01-13 paper-Ro_Man-2016.tex
@@
 
+\usepackage[pdftex]{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
+%\graphicspath{}
+%\usepackage[utf8]{inputenc}
+
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric, arrows}
+
+\tikzstyle{io} =[text centered, draw=black]
+\tikzstyle{process} = [text centered, text width=1cm, draw=black]
+\tikzstyle{arrow} = [thick,->,>=stealth]
+\tikzstyle{darrow} = [thick,<->,>=stealth] 
+\tikzstyle{io2} =[ text centered, draw=black]
+\tikzstyle{process2} = [text width=2cm, draw=black]
+
+\usepackage{paralist}
+\usepackage{amsfonts}
+\usepackage{hyperref}
+
+\usepackage{url}
+\usepackage{booktabs}
+
+\usepackage{tikz}
+\usetikzlibrary{positioning, calc}
+\usetikzlibrary{shapes.geometric, arrows}
+% COLORS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{color}
+\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
+\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
+%\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
+\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}
+\definecolor{editorOcher}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
+\definecolor{editorGreen}{rgb}{0, 0.5, 0} % #007C00 -> rgb(0, 124, 0)
+\definecolor{orange}{rgb}{1,0.45,0.13}		
+\definecolor{olive}{rgb}{0.17,0.59,0.20}
+\definecolor{brown}{rgb}{0.69,0.31,0.31}
+\definecolor{purple}{rgb}{0.38,0.18,0.81}
+\definecolor{lightblue}{rgb}{0.1,0.57,0.7}
+\definecolor{lightred}{rgb}{1,0.4,0.5}
+
+\usepackage[draft,nomargin,footnote]{fixme}
+
+\graphicspath{{figs/}}
+
+%\usepackage{xspace}
+
 \title{\LARGE \bf
-Influence of child-robot spacial arrangement in a learning by teaching task}
+Child-Robot Spatial Arrangement in a Learning by Teaching Activity}
 
-\author{A1$^{1}$ and A2$^{2}$% <-this % stops a space
+\author{Wafa Johal$^{1}$, Alexis Jacq$^{1}$$^{2}$, Ana Paiva$^{2}$ and Pierre Dillenbourg$^{1}$  % <-this % stops a space
 \thanks{}% <-this % stops a space
-\thanks{$^{1}$A1 is with Faculty of A1,
-        University of A1, country
-        {\tt\small A1 email}}%
-\thanks{$^{2}$A2 is with Faculty of A2,
-        University of A2, country
-        {\tt\small A2 email}}%
+\thanks{$^{1}$ CHILI Lab,
+        École Fédérale Polytechnique Lausanne, Switzerland
+        {\tt\small firstname.lastname@epfl.ch}}%
+\thanks{$^{2}$Instituto Superior T\'{e}cnico, University of Lisbon, Portugal
+        {\tt\small firstname.lastname@inesc-id.pt}}%
 }
@@
 \maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
 
@@
 \begin{abstract}
-In this paper we present a study in which we test the influence of child-robot spatial arrangement on child's focus of attention, child's perception of robot's performance in the CoWriter learning by teaching activity.
-In this activity the child teaches a Nao obot how to handwrite. 
-In our study, we explore two spatial condition from Kendon's F formation, the side-by-side and the face-t-face formations.
-
-We have 3 conditions following Kendon's F formation: 
-\begin{itemize}
-\item side by side
-\item face to face
-\item in L shape
-\end{itemize}
-
+In this paper, we present an experiment in the context of a child-robot interaction where we study the influence of the spatial arrangement of the interaction on the child's focus of attention and the perception of the robot's performance in the ``''Co-Writer learning by teaching'' activity.
+In this activity, the child teaches a Nao robot how to write by hand.
+Typically in a educational child robot interaction, face-to-face spatial arrangements are usually set.
+We explored two spatial conditions from Kendon's F-formation, the side-by-side and the face-to-face formations in a within subject experiment.
+We estimated the gaze behaviour of the child and the consistency of their grading of the robot with regard to the robot's progress in writing. 
+Even-though the demonstrations provided by children were not different between the two conditions (i.e.
+the robot's learning didn't differ),  the results showed that in the side-by-side condition children tended to be more indulgent with the robot's mistakes and to give it better feedback.
+These results will allow us to take into account the variability of the judgement of the children relatively to the robot's performances.
 \end{abstract}
@@
 \section{INTRODUCTION}
-Cowriter
 
-In this activity the child plays the role of a teacher.
+Application of robots in learning tasks has been increasing and has shown very promising results these past ten years. 
+R-learning, in reference to e-learning, aims to design robots that would be helpful for learning.
+In our research context, we consider the problem of how robots could enhance the effectiveness of education.
+The potential of robots for individual adaptation and their ability to handle repetitive tasks makes them fit well in the educational world.
+In that vein, the Co-Writer projects aims to help children with difficulties in handwriting \cite{hood2015when}.
+It is based on the idea of ``learning by teaching''.
+Under this paradigm, by teaching a robot (the Nao, in our case) how to write, children learn and improve their handwriting at the same time.
+The activity also plays with the protégé effect, which makes children more motivated in practising for the robot than for themselves.
+
+Previous studies in the Co-Writer project helped to develop a system that generates handwriting for the robot based on demonstrations from the child\cite{hood2015when}.
+Case studies presented in \cite{jacq2016building} showed that children were able to stay engaged in long term interactions with repeated sessions within the Co-Writer activity in real pedagogical/therapeutic contexts.
+These works proved to have a positive effect on the extrinsic motivation of the children when practising their handwriting, thanks to the protégé effect.
+
+Authors in \cite{Matsuzoe2012} had a similar approach to learning by teaching with their Care Receiving Robot, who was being taken care of and taught by a child using physical interaction. 
+In this study, authors chose to investigate handwriting (or drawing shapes) as well, but with a more physical based approach.
+In their experimental setting, the child would teach handwriting to the robot by placing himself behind the robot and moving it's hand.
+This study varied from other works in educational human-robot interaction in a way that the child was not only facing the robot but would act as a care-taker rather than a teacher.
+
+As robots are entering our living space, they must adapt to our social norms.
+These norms vary from politeness to unspoken social rules (as for instance, the personal space of a person).
+In home environments, robots will be expected to perform their functions in a manner that is clearly understandable and predictable by the humans around.
+This requires adaptive personalisation of the robot to the individual needs of the humans, but also to the task being performed currently.
+Some previous studies have shown that the spatial setting with a robot was also a way to convey non-verbal messages and it serves to influence the relationship with the user\cite{Takayama2009,kristoffersson2013measuring}.
+
+In this study, we want to explore the effect of spatial arrangement on the child-robot interaction within the Co-Writer activity.
 
 \section{RELATED WORKS}
-Proxemics
+Spatial configuration is part of non-verbal cues of interpersonal stance.
+Spatial arrangement is also a social signal that tells about the relationship between people.
+Hall \cite{hall} has proposed to divided the interpersonal space according to the distance between the individuals (intimate - the closer, personal social and public).
 
-Role attribution
+Kendon \cite{Kendon2010} called the F-Formation a spatial-orientational system that aims to explain how people arrange themselves in a group interaction.
+%According to Kendon, the way people arrangement themselves during an interaction reflects their engagement and involvement with the other persons. 
+Kendon proposed three main F-formations : face-to-face (or vis-a-vis), L shape and side-by-side. These formations are illustrated by Figure \ref{fig:fformations}.
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.2\textwidth}
+		\centering
+		\includegraphics[width=0.8\linewidth]{./figures/fformationff.png}
+		\caption{Face to face}
+		\label{fig:ff}
+	\end{subfigure}%
+	\begin{subfigure}{0.2\textwidth}
+		\centering
+		\includegraphics[width=0.8\linewidth]{./figures/fformationL.png}
+		\caption{L-Shape}
+		\label{fig:lshape}
+	\end{subfigure}
+	\begin{subfigure}{0.2\textwidth}
+		\centering
+		\includegraphics[width=0.8\linewidth]{./figures/fformationss.png}
+		\caption{Side by Side }
+		\label{fig:sidebside}
+	\end{subfigure}
+	\caption{Three possible Kendon's F-formations around a rectangular table}
+	\label{fig:fformations}
+\end{figure}
 
-Kendon F Formation in HRI
-\cite{huttenrauch2006investigating}
+According to \cite{knapp2013nonverbal}, spatial arrangement and seating position can determine a person's role in a group.
+It could also predispose the person to either competitive (face to face) or cooperative (side by side) mental setting in a shared task.
 
-We propose to study the impact of spatial arrangement on engagement of children a handwriting task
-\section{APPROACH}
+In educational child-robot interaction, quite often, the robot is placed as a tutor or a peer helping the child, and uses social capabilities to enhance the learning \cite{Saerbeck2010}.
+Kanda \cite{Kanda2004} reported an experiment involving children that learns from a robot as they would from a peer.
+In this other experiment,
+\cite{Leyzberg2014} showed in a face to face setting that the physical presence of the robot produced measurable learning gains.
+\cite{Kennedy2015} confirmed these results but recommended caution when applying social behaviours in a tutoring context. 
+%explain why caution
 
-within subject, 2 robots in front of the child who has to teach to the two robots
+Spatial arrangements have been studied in previous research\cite{Kuzuoka,huttenrauch2006investigating,vazquez2014spatial} in HRI, often as a challenge of path planning, or as a metric but less frequently as a non-verbal cue of communication in a learning task.
 
-Hypothesis
-\begin{itemize}
-\item Child feels more in a teacher student relationship when facing the robot
-\item child feels more in a peer to peer when the robot is in L or side by side 
-\item how does it influence the engagement -> with-me-ness
-\item  does the child looks more at the experimenter when the robot is badly behaving
-\item how does the child rates the robots performances according to  the arrangement
-\end{itemize}
+We propose to study the impact of spatial arrangement on the engagement of children in a handwriting task.
+We performed a study in a school with 12 children performing the same teaching task under two conditions.
+The child was either facing the robot (similar to other tutoring experiments) or was sitting next to the robot (as a peer teaching setup).
+
+%We also wanted to study the influence of being in a group or alone when interacting with the robot.
+%At the difference from the group configuration, in the group configuration, other children were witnessing the interaction with the child.
 
 \section{METHOD}
+The experiment took place in a primary school in Switzerland where children are taught in English.
+In this experiment, we targeted children aged 5 who start handwriting at that age, but do not typically master it yet.
+The children interacted with the robot under two conditions of the F-Formation in a random order.
+
+Our goal was to investigate the effect of spatial arrangement on the interaction.
+We expected that children would give better feedback to the
+when teaching it in a side-by-side configuration for several reasons.
+The side-by-side arrangement corresponds to a peer teaching arrangement, unlike the face-to-face teaching arrangement, which is more frequent seen in a teacher-student relationship.
+Also, in the side-by-side formation, the robot and the child have the same perspective of the shared tablet on which they write.
+Perspective sharing is an ability that facilitates mutual understanding \cite{berlin2006perspective}.
+Hence by having the robot and the child side-by-side, the mutual understanding would be eased.
+
+\subsection{Participants and Apparatus}
+12 subjects (six girls) from the same classroom (aged 5 to 6 y.o.) participated to the within subject study.
+The two considered F-formations for this experiment are presented in the Figure~\ref{fig:test}: face-to-face~\ref{fig:sub1} and side-by-side~\ref{fig:sub2}.
+Children were presented the two conditions sequentially with and interval of three days in a counterbalanced manner.
+
+\begin{figure*}
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=0.8\linewidth]{./figures/f2f_photot.png}
+  \caption{Face to face spatial formation}
+  \label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=0.8\linewidth]{./figures/s2s_photo2t.jpg}
+  \caption{Side by Side spatial formation}
+  \label{fig:sub2}
+\end{subfigure}
+ \caption{Experimental set-ups showing the \emph{with-me-ness} targets in the rectangles: orange - the writing tablet,  blue - the robot's head, green - the tablet used to select a word to teach to the robot}
+\label{fig:test}
+\end{figure*}
+Apart from this change in the spatial setting, the interaction was kept the same. 
+The children were told they had to teach the robot how to write some words. 
+We briefly presented the two tablet interfaces and the interaction started.
+Any word from a list displayed on the selection tablet could be picked by the child.
+As the robot would start to write this word, it was set to be a very bad writer at the beginning of the first session for each child.
+The child could then give a feedback to the robot by pressing either a thumbs up or a thumbs down button.
+The child would then use a pen and demonstrate how to write the word and the robot would then rewrite the word using the demonstration of the child.
+The generated writing of the robot was computed to be halfway from its previous writing state and the new demonstration provided by the child.
+
+Several hypothesis were made concerning the influence of the spatial arrangement on the interaction.
+We expected that the gaze behaviour of the child would vary according to the spatial configuration.
+More gazing at the robot's head would be eased in the face-to-face condition.
+Our research question was to measure the degree to which this also influenced the way children behaved as a teacher (were they more or less severe with the robot facing them)
+Because of this influence of facing the robot and being able to see its head, we also believed that the robot would be perceived as more competent in the face to face condition and hence collect more positive feedback from the child.
+Indeed some previous studies have shown that social appearance \cite{goetz2003matching} has an influence on the perceived competences.
+
+The engagement of the child in the task can also be influenced by the arrangement.
+For that particular aspect, we will measure the number of repetitions of each word, as well as the with-me-ness, which is discussed in the following section.
+
+\subsection{With-me-ness}
+The with-me-ness introduced in HRI by \cite{lemaignan2016realtime}, helps to set specific targets during each state of the interaction and to determine whether the user is looking at one of these targets or not.
+The algorithm is based on the \textit{d-lib library} that helps to estimate the head pose of the user using a video from a webcam device for instance.
+From this head pose, the visual focus of attention (VFoA) is computed.
+The inclusion of the targets in the VFoA allows then to compute the with-me-ness.
+In a simple way, the with-me-ness value will increase if the child looks at the specific set of targets, or else it decreases.
+This measure allows us to see if the child is engaged in the interaction and is looking at the tablet or the robot's head when he/she should.
+This measure is actually very close to the notion of synchrony already studied in HRI \cite{delaherche2012interpersonal}, where bounding between individuals is reflected by their ability to synchronize in the task (look at the same time at the same targets).
+
+For this experiment, the targets where: "the observer"(a teacher or a teacher assistant),"the experimenter",  "the selection tablet"(the tablet used to pick a word) and the "tablet".
+The with-me-ness is initially set to 0.5 and takes values from 0 to 1.
+According to the state in which the activity is, (robot is writing, child is writing,\dots) the with-me-ness will be increased if the child looks at a target that is in the set of targets that are optimum within this particular state of the activity.
+We record these targets and the with-me-ness at a frequency of about $1Hz$.
+
+The targets are defined according to their spatial relation with the camera used (placed on the table at the robot's feet).
+The position of the targets was changed according to the F-formation condition, but the camera stayed at the same position
+Figure \ref{fig:test} shows these targets for the two conditions.
+
+%todo boucle avec Hypo
+
+\subsection{Reward Mechanism}
+The tablet interface on which the child and the robot practice their handwriting also contains two buttons that allow the child to give a positive (green thumb-up) or negative (red thumb-down) feedback to the robot's handwriting.
+After every trial of the robot, the child could click on these feedback buttons as much as he/she wants.
+We monitored each of these clicks.
+
+These clicks aimed to assess the child's perception of the robot's progress.
+When converging to a better writing we expect the child to give better feedback.
+However, these buttons could also be used by the child as an encouragement method and children could give a positive feedback even though the robot didn't make progress.
+
+\subsection{Performances}
+As the child was managing which word the robot would learn, he/she could also provide as many demonstrations as he/she wanted.
+The child was also free to change the word when satisfied with the robot's performance.
+
+\subsubsection{Response Time and Writing Time}
+We recorded the time spent on the writing and the response time for each word demonstrated by the children.
+We also monitored the number of demonstrations provided by the child for each word.
+These measure were cues to how dedicated the child was in the task
+
+\subsubsection{Writing Score for the Robot}
+%Regularity of writing in time
+Since the learning algorithm took as input the child's demonstration, if the child provided repeatedly the exact same demonstration, then the robot would converge faster to their handwriting.
+This score is hence a hint on children's regularity, with the underlying assumption that a child is sure of the fact that his handwriting is more regular.
+Also, since children are teaching the robot, they might judge the robot's handwriting according to their provided demonstration.
+
+The score for the generated letter by the robot was obtained by the distance between the same demonstrated letter by the child and the generated letter.
+We finally computed the evolution of this score compare to the previous for each demonstrated word.
+We then represented the evolution of the robot's handwriting with different states:
+'S=': the first trial of this word by the robot, 'S-': the score decreases and 'S+' the score increases.
 
 \section{RESULTS}
+%The effect of IV on DV was statistically significant ($F_{a,b}= C, p<d*$). 
+%The effect of IV on DV was not statistically significant ($F_{a,b}= C, ns$). 
+In this section, we present results from this study on 12 children that interacted with the robot twice in the two conditions (side-by-side and face-to-face).
+We studied the impact on the F-formation on the reward given with the buttons, the performance and the with-me-ness.
 
-\subsection{Seriousness}
+\subsection{Reward Mechanism}
+Children well understood that they were teaching the robot and often gave bad scores for the first untrained trial of the robot.
+Children gave feedback with an average of 3 feedbacks per demonstration.
+Figure \ref{fig:uf_nb} shows the evolution of the sum of feedbacks given for all repeated word for each demonstration.
+We noticed that the feedback is first negative and grows towards a positive feedback after each demonstration.
+Children usually gave a positive feedback just before changing the word taught to the robot.
+
+  \begin{figure}
+  	\centering
+  	\includegraphics[width=0.8\linewidth]{figures/plots/evoldemo}
+  	\caption{Evolution of Feedback along the demonstration index}
+  	\label{fig:uf_nb}
+  \end{figure}
+
+ The effect of the F-Formation on the feedback from the child was statistically significant ( $F_{1,272}= 4.396, p<0.05$).
+As, illustrated on Figure \ref{fig:userfeedback_fformation_se}, the average feedback per demonstration was greater($M=0.03, SD=1, N=147$) for the side-by-side condition compare to the face-to-face condition ($M=-0.23, SD=0.98, N=138$).
+ \begin{figure}
+ 	\centering
+ 	\includegraphics[width=0.6\linewidth]{figures/plots/userfeedback_fformation_se}
+ 	\caption{Feedback According to the F-Formation}
+ 	\label{fig:userfeedback_fformation_se}
+ \end{figure}
+
+Children kept giving feedback along the interaction and no drop in the number of feedbacks was observed during the experiment.
+They took their duty to teach the robot seriously in that way.
+
+We also observe an order effect showing that children tended to give higher feedback in the second session compare to the first one.
+%todo see if add significance here 
+This can simply be explained by the fact that the robot's learning state was progressive between the two session. 
+The robot didn't start to learn from scratch in the second session but had already some knowledge from the first session with this same child.
 
 \subsection{With-me-ness}
-Present it as a measure of synchrony,
+Generally, children understood the dynamics of the interaction, as in general the with-me-ness stayed above 0.5 throughout the interaction (started et 0.5 but always finished above).
+\begin{figure}	
+\centering
+\includegraphics[width=0.6\linewidth]{figures/plots/withmeness_fformation_ci}
+\caption{With-me-ness According to the F-Formation (Means and Confidence Intervals)}
+\label{fig:withmeness_fformation_ci}
+\end{figure}
+ The effect of the F-Formation on the with-me-ness of the child was statistically significant ( $F_{1,15983}= 293.2, p<0.001$).
+The with-me-ness was greater($M=0.79, SD=0.18, N=7722$) for the face-to-face condition compare to the side-by-side condition ($M=-0.72, SD=0.21, N=8267$) (see Figure \ref{fig:withmeness_fformation_ci}).
+ This result was expected, as the robot was facing the robot, its face was more visible for the child.
 
-Get time when robot looking where and see if similar pattern with child
+Again, we observed an order effect with the withmeness increasing between the two session. 
+As children were more confordable with the system, it is logic that they started to learn the dynamics of the interaction knwoing when to look at the selection tablet, the writing tablet and the robot.
+%todo add stats
+%	session	N	new_w	sd	se	ci
+%	1	1	8886	0.7248584	0.2175269	0.002307596	0.004523421
+%	2	2	7103	0.7965673	0.1691839	0.002007419	0.003935140
+%Error: Within
+%Df Sum Sq Mean Sq F value Pr(>F)    
+%session       1   12.8  12.797   339.8 <2e-16 ***
+%Residuals 15985  602.0   0.038
 
 \subsection{Performances}
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.4\linewidth]{figures/plots/score_alone_se}
+%\caption{Learning speed According to group or alone modality}
+%\label{fig:score_alone_ci}
+%\end{figure}
+\subsubsection{Response Time and Writing Time}
+Figure \ref{fig:times} shows on the left the average number of demonstration for each word thought to the robot for the two spatial arrangement conditions. 
+There was no significant difference between the conditions even-though the average number of demonstration given by the child in the side-by-side condition seems higher than the face-to-face.
 
-\subsection{Questionnaire on likeability and Interrelationship}
+The centrer graph of Figure \ref{fig:times} shows the average response time for the demonstration provided by the children for the two spatial arrangement conditions.
+The response time is the delay between the time when the robot finishes to write and the time when the child touches the tablet.
+There was no significant difference between the conditions.
 
-\section{CONCLUSIONS}
+The writing time (right graph on Figure \ref{fig:times}) corresponds to the delay between the time when the robot finishes its trial and the time the child finishes its new demonstration or changes word.
+This time also include the moment in which the child can give a feedback via the buttons.
+No significant difference in the writing time was found.
 
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
+\begin{figure*}[ht]
+	\centering
+	\includegraphics[width=0.25\linewidth]{figures/plots/repetition_fformation_ci}
+	\includegraphics[width=0.25\linewidth]{figures/plots/responseTime_fformation_ci}
+	\includegraphics[width=0.25\linewidth]{figures/plots/writingTime_fformation_ci2}
+	\caption{Number of demonstration per word (left), response time (center), writing time (right) - (Means and Confidence Intervals)}
+	\label{fig:times}
+	\end{figure*}
+
+These results show that children when not spending more time per word in one condition of the other. 
+The spatial condition didn't influence the involvement of the child in the task. 
+% The effect of the group variable on the score of the child was statistically significant ( $F_{1,279}= 6.928, p<0.01$).
+The score was greater($M=0.41, SD=0.11, N=141$) in  the alone condition compare to the group condition ($M= 0.37, SD=0.11, N=140$).
+%These results confirm the fact that the robot is better suited here for individual interaction. 
+\subsubsection{Writing Score for the Robot}
+There was no significant difference of score in the F-formation condition tested (side-by-side:$M=0.80, SD=0.08, N=135$, face-to-face: $M=0.79, SD=0.08, N=191$).
+This result means that the children were teaching as well in the face-to-face condition as in the side-by-side condition.
+However, results showed significant differences in terms of feedback given to the robot regarding the score of the robot.
+Table~\ref{proba} shows the probabilities of transition from after the score increases and after the score decreases.
+When the score increases, we see that in the face-to-face condition, the probability of positive feedback is smaller than in the side-by side condition.
+On the contrary, the probability of having a negative feedback after the score having decreased is higher in the face-to-face condition.
+We can also notice that when the score decreases, the probability of having a positive feedback is twice higher in the side-by-side condition
+
+\begin{table}[ht!]
+\centering
+\caption{\small Probability of feeback given the score per word in  the two conditions : face-to-face / \emph{side-by-side}}
+\label{proba}
+\begin{tabular}{l|p{2cm}|p{2cm}l@{}}
+\toprule
+Score event & Positive Feedback & Negative Feedback \\
+\midrule
+Score Increases & 	0.16 / \emph{0.27}	& 0.46 / \emph{0.47} \\
+Score Decreases &	0.15 / \emph{0.32}	& 0.42 / \emph{0.28} \\
+\bottomrule
+\end{tabular}
+\end{table}
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\linewidth]{./figures/faceface_score}
+		\caption{Face to face spatial formation}
+		\label{fig:f2fstate}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\linewidth]{./figures/sidebiside_score}
+		\caption{Side by Side spatial formation}
+		\label{fig:sbsstate}
+	\end{subfigure}
+	\caption{Transitions states from Score evolutions ($S+$ : score increases compared to previous score, $S-$: score decreases compare to the previous) to children's feedback}
+	\label{fig:state}
+\end{figure*}
+
+All the transitions between the scores and the feedback buttons are illustrated on Figure \ref{fig:state}
+Children were displaying a more positive attitude towards the robot when placed in side-by-side position.
+This positive attitude was showed by rewarding more improvements of the robot and also penalising less the retrogression of the robot's writing.
+Children even rewarded retrogression more often in the side-by-side condition.
+
+\section{DISCUSSIONS AND CONCLUSIONS}
+In this paper we presented a study that aimed to elicit the effect of spatial arrangement on a learning task between a robot and a child.
+Spatial configuration has never to our knowledge been studied in terms of effect on the task but usually in the context of the social interaction.
+In this experiment, we showed that this spatial arrangement could also have an influence in the task and on how the child was behaving as a teacher.
+Our results showed that even if the robot's learning didn't vary between the side-by-side and the face-to-face condition, the feedback from the child was varying.
+This suggests that the relationship between the child and the robot was different between the conditions.
+These results are in line with the literature in spatial arrangement and non-verbal social cues.
+
+We noticed that the children were expecting the robot to react to the feedback.
+We are working on different form of reactions for future experiments to allow the robot to react according to the feedback from the child and also in perspective with the fairness of the feedback regarding the score of the robot.
+For instance, if the child gives a positive feedback when the robot is actually improving, the robot should display a positive emotion.
+If it is given a positive feedback but does not actually make any progress, he might express doubt to force the child to be more exigent.
+
+Some limitations are however to be noticed. 
+In this experiment, the robot was moving only when writing. 
+Even if our results showed that the side-by-side elicited more positive feedback from the children, in the case where the robot would display some emotional reaction during the interaction, the same effect might not be observed.
+We plan to enhance the interaction with such reaction and to research the effect of such reactions on the child's perception of the robot's progresses. 
+Long term studies might also bring more insights to theses results in order to see if the effect of the spatial arrangement sustain over time.
+%discuss results regarding the literature, same ? different arguments for/against initial premise, limitations, etc.
+
+%\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                   % on the last page of the document manually. It shortens
@@
 \section*{ACKNOWLEDGMENT}
+This research was partially supported by the Funda\c{c}\~{a}o para a Ci\^{e}ncia
+e a Tecnologia (FCT) with reference UID/CEC/ 50021/2013, and by the Swiss
+National Science Foundation through the National Centre of Competence in
+Research Robotics.
 

### 2016-05-23 paper-Ro_Man-2016.tex
taking review into account, todo proof reading, last section and redo figure and discussion

@@
 Any word from a list displayed on the selection tablet could be picked by the child.
-As the robot would start to write this word, it was set to be a very bad writer at the beginning of the first session for each child.
-The child could then give a feedback to the robot by pressing either a thumbs up or a thumbs down button.
+As the robot would start to write this word. It was set to be a very bad writer at the beginning of the first session for each child.
+The child could then give a feedback to the robot by pressing thumbs up or a thumbs down buttons how many time they wanted.
 The child would then use a pen and demonstrate how to write the word and the robot would then rewrite the word using the demonstration of the child.
@@
 
-Several hypothesis were made concerning the influence of the spatial arrangement on the interaction.
+Several hypotheses were made concerning the influence of the spatial arrangement on the interaction.
 We expected that the gaze behaviour of the child would vary according to the spatial configuration.
-More gazing at the robot's head would be eased in the face-to-face condition.
-Our research question was to measure the degree to which this also influenced the way children behaved as a teacher (were they more or less severe with the robot facing them)
-Because of this influence of facing the robot and being able to see its head, we also believed that the robot would be perceived as more competent in the face to face condition and hence collect more positive feedback from the child.
-Indeed some previous studies have shown that social appearance \cite{goetz2003matching} has an influence on the perceived competences.
+More gazing at the robot's head would be expected in the face-to-face condition.
+Our research question was to measure the degree to which this also influenced the way children behaved as a teacher (were they more or less severe with the robot facing them).
+As children give a feedback to the robot for each demonstratation, we intend to measure if there is any difference between vis-a-vis and side-by-side regarding this feedback (does the side-by-side condition trigger more positive feedback?).
+%Because of this influence of facing the robot and being able to see its head, we also believed that the robot would be perceived as more competent in the face to face condition and hence collect more positive feedback from the child.
+%Indeed some previous studies have shown that social appearance \cite{goetz2003matching} has an influence on the perceived competences.
 
@@
 For that particular aspect, we will measure the number of repetitions of each word, as well as the with-me-ness, which is discussed in the following section.
+Since children were quite young, we choose to not use any self-reported measures or questionnaires.
 
 \subsection{With-me-ness}
-The with-me-ness introduced in HRI by \cite{lemaignan2016realtime}, helps to set specific targets during each state of the interaction and to determine whether the user is looking at one of these targets or not.
+The with-me-ness introduced in HRI by \cite{lemaignan2016realtime}, helps to set specific targets during each state of the interaction and to determine whether the user is looking at one of these attentional targets or not.
 The algorithm is based on the \textit{d-lib library} that helps to estimate the head pose of the user using a video from a webcam device for instance.
 From this head pose, the visual focus of attention (VFoA) is computed.
-The inclusion of the targets in the VFoA allows then to compute the with-me-ness.
-In a simple way, the with-me-ness value will increase if the child looks at the specific set of targets, or else it decreases.
+The inclusion of the targets in the VFoA allows then to compute the \emph{with-me-ness}.
+In a simple way, the \emph{with-me-ness} value will increase if the child looks at the specific set of targets, or else it decreases.
 This measure allows us to see if the child is engaged in the interaction and is looking at the tablet or the robot's head when he/she should.
+Indeed, in our learning by teaching activity, the robot has also a hidden pedagological role. It's progress aim actually to make the child practice and think about his/her own way of writing. 
+In that sens, we can set attentional targets as proposed by \cite{sharma2014me} when the \emph{with-me-ness} was first introduced for Computer Supported Collaborative Learning.
+
 This measure is actually very close to the notion of synchrony already studied in HRI \cite{delaherche2012interpersonal}, where bounding between individuals is reflected by their ability to synchronize in the task (look at the same time at the same targets).
 
-For this experiment, the targets where: "the observer"(a teacher or a teacher assistant),"the experimenter",  "the selection tablet"(the tablet used to pick a word) and the "tablet".
+For this experiment, the targets were: "the observer"(a teacher or a teacher assistant),"the experimenter",  "the selection tablet"(the tablet used to pick a word) and the "tablet".
 The with-me-ness is initially set to 0.5 and takes values from 0 to 1.
@@
 We record these targets and the with-me-ness at a frequency of about $1Hz$.
+The evolution of the withmeness is computationaly attenuated in order to remove noisy data and we set a weight on the update at 10\% (90\% is the previous state).
 
@@
 %Regularity of writing in time
-Since the learning algorithm took as input the child's demonstration, if the child provided repeatedly the exact same demonstration, then the robot would converge faster to their handwriting.
-This score is hence a hint on children's regularity, with the underlying assumption that a child is sure of the fact that his handwriting is more regular.
-Also, since children are teaching the robot, they might judge the robot's handwriting according to their provided demonstration.
+Since the learning algorithm took as input the child's demonstration, if the child provided repeatedly the exact same demonstration, then the robot would converge faster to his/her handwriting.
+This score is hence a hint on children's regularity, with the underlying assumption that the regularity handwriting is a sign of progress.
+Since children are teaching the robot, they may judge the robot's handwriting according to their provided demonstration, and compare simply their demonstration with the robot's.
 
-The score for the generated letter by the robot was obtained by the distance between the same demonstrated letter by the child and the generated letter.
-We finally computed the evolution of this score compare to the previous for each demonstrated word.
-We then represented the evolution of the robot's handwriting with different states:
-'S=': the first trial of this word by the robot, 'S-': the score decreases and 'S+' the score increases.
+At each demonstration of the robot, we were calculating a \emph{writing score}. 
+Each demonstration was encoded as a list of seventy 2D points.
+This \emph{writing score} is the euclidian distance between the demonstrated letter by the child and the generated letter by the robot.
+
+We also computed the evolution of this score at each demonstration.
+We represent the evolution of the robot's handwriting with different states:
+'S=': the first trial of this word by the robot, 'S-': the score is decreasing and 'S+' the score is increasing. 
+If the child change a lot his/her way of writing between consecutives demonstration, the score would then deacrease.
+In the contrary, the regularity of the demonstration would make the score increase rapidly.
 
@@
 Children gave feedback with an average of 3 feedbacks per demonstration.
-Figure \ref{fig:uf_nb} shows the evolution of the sum of feedbacks given for all repeated word for each demonstration.
+Figure \ref{fig:uf_nb} shows the average evolution along the demonstrations of the sum of feedbacks given for all children.
 We noticed that the feedback is first negative and grows towards a positive feedback after each demonstration.
@@
 \subsubsection{Response Time and Writing Time}
-Figure \ref{fig:times} shows on the left the average number of demonstration for each word thought to the robot for the two spatial arrangement conditions. 
+Figure \ref{fig:times} shows on the left the average number of demonstration for each word taught to the robot for the two spatial arrangement conditions. 
 There was no significant difference between the conditions even-though the average number of demonstration given by the child in the side-by-side condition seems higher than the face-to-face.
@@
 	\end{subfigure}
-	\caption{Transitions states from Score evolutions ($S+$ : score increases compared to previous score, $S-$: score decreases compare to the previous) to children's feedback}
+	\caption{Transitions states from score evolutions ($S+$ : score increasing compared to previous score, $S-$: score decreasing compare to the previous) to children's feedback (thumb up: positive feedback, thumb down : negative feedback, and no feedback given)}
 	\label{fig:state}
@@
 
+\small
 \bibliographystyle{abbrv}

### 2016-05-24 paper-Ro_Man-2016.tex
start proofreading

@@
 \begin{abstract}
-In this paper, we present an experiment in the context of a child-robot interaction where we study the influence of the spatial arrangement of the interaction on the child's focus of attention and the perception of the robot's performance in the ``''Co-Writer learning by teaching'' activity.
-In this activity, the child teaches a Nao robot how to write by hand.
-Typically in a educational child robot interaction, face-to-face spatial arrangements are usually set.
+In this paper, we present an experiment in the context of a child-robot interaction where we study the influence of the child-robot spatial arrangement on the child's focus of attention and the perception of the robot's performance in the ``''Co-Writer learning by teaching'' activity.
+In this activity, the child teaches a Nao robot how to handwrite.
+In an educational child robot interaction, face-to-face spatial arrangements are usually set.
 We explored two spatial conditions from Kendon's F-formation, the side-by-side and the face-to-face formations in a within subject experiment.

### 2016-05-24 paper-Ro_Man-2016.tex
ready for rpoof reading

@@
 \usetikzlibrary{shapes.geometric, arrows}
-% COLORS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \usepackage{color}
@@
 \begin{abstract}
-In this paper, we present an experiment in the context of a child-robot interaction where we study the influence of the child-robot spatial arrangement on the child's focus of attention and the perception of the robot's performance in the ``''Co-Writer learning by teaching'' activity.
-In this activity, the child teaches a Nao robot how to handwrite.
-In an educational child robot interaction, face-to-face spatial arrangements are usually set.
-We explored two spatial conditions from Kendon's F-formation, the side-by-side and the face-to-face formations in a within subject experiment.
-We estimated the gaze behaviour of the child and the consistency of their grading of the robot with regard to the robot's progress in writing. 
+In this paper, we present an experiment in the context of a child-robot interaction where we study the influence of the child-robot spatial arrangement on the child's focus of attention and the perception of the robot's performance.
+In the ``''Co-Writer learning by teaching'' activity, the child teaches a Nao robot how to handwrite.
+Usually only face-to-face spatial arrangements are tested in educational child robot interactions, but we explored two spatial conditions from Kendon's F-formation, the side-by-side and the face-to-face formations in a within subject experiment.
+We estimated the gaze behaviour of the child and their consistency in grading the robot with regard to the robot's progress in writing. 
 Even-though the demonstrations provided by children were not different between the two conditions (i.e.
 the robot's learning didn't differ),  the results showed that in the side-by-side condition children tended to be more indulgent with the robot's mistakes and to give it better feedback.
-These results will allow us to take into account the variability of the judgement of the children relatively to the robot's performances.
+These results highlight the influence of experimental choices in child-robot interaction.
+%These results will allow us to take into account the variability of the judgement of the children relatively to the robot's performances.
 \end{abstract}
@@
 Application of robots in learning tasks has been increasing and has shown very promising results these past ten years. 
-R-learning, in reference to e-learning, aims to design robots that would be helpful for learning.
-In our research context, we consider the problem of how robots could enhance the effectiveness of education.
+\emph{R-learning}, in reference to e-learning, aims to design robots that would be helpful for learning.
+%In our research context, we consider the problem of how robots could enhance the effectiveness of education.
 The potential of robots for individual adaptation and their ability to handle repetitive tasks makes them fit well in the educational world.
@@
 It is based on the idea of ``learning by teaching''.
-Under this paradigm, by teaching a robot (the Nao, in our case) how to write, children learn and improve their handwriting at the same time.
-The activity also plays with the protégé effect, which makes children more motivated in practising for the robot than for themselves.
+Under this paradigm, by teaching a robot (Nao from Aldebaran) how to write, children learn and improve their handwriting at the same time.
+The activity also plays with the \emph{protégé effect}, which makes children more motivated in practising for the robot than for themselves.
 
@@
 In home environments, robots will be expected to perform their functions in a manner that is clearly understandable and predictable by the humans around.
-This requires adaptive personalisation of the robot to the individual needs of the humans, but also to the task being performed currently.
-Some previous studies have shown that the spatial setting with a robot was also a way to convey non-verbal messages and it serves to influence the relationship with the user\cite{Takayama2009,kristoffersson2013measuring}.
+This requires adaptive personalisation of the robot to the individual needs of the humans, but also to the task being currently performed.
+Some previous studies showed that the spatial setting with a robot was also a way to convey non-verbal messages and it serves to influence the relationship with the user\cite{Takayama2009,kristoffersson2013measuring}.
+Spatial arrangement is still a factor relatively unexplored in HRI and its influence on the interaction is still unclear.
 
-In this study, we want to explore the effect of spatial arrangement on the child-robot interaction within the Co-Writer activity.
+In this study, we explore the effect of spatial arrangement on the child-robot interaction within the Co-Writer activity.
 
@@
 Spatial arrangement is also a social signal that tells about the relationship between people.
-Hall \cite{hall} has proposed to divided the interpersonal space according to the distance between the individuals (intimate - the closer, personal social and public).
-
 Kendon \cite{Kendon2010} called the F-Formation a spatial-orientational system that aims to explain how people arrange themselves in a group interaction.
@@
 Kendon proposed three main F-formations : face-to-face (or vis-a-vis), L shape and side-by-side. These formations are illustrated by Figure \ref{fig:fformations}.
-\begin{figure}
+\begin{figure}[h!]
 	\centering
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{./figures/fformationff.png}
+		\includegraphics[width=0.75\linewidth]{./figures/fformationff.png}
 		\caption{Face to face}
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{./figures/fformationL.png}
+		\includegraphics[width=0.75\linewidth]{./figures/fformationL.png}
 		\caption{L-Shape}
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{./figures/fformationss.png}
+		\includegraphics[width=0.75\linewidth]{./figures/fformationss.png}
 		\caption{Side by Side }
@@
 In this other experiment,
-\cite{Leyzberg2014} showed in a face to face setting that the physical presence of the robot produced measurable learning gains.
+\cite{Leyzberg2014} showed in a face-to-face setting that the physical presence of the robot produced measurable learning gains.
 \cite{Kennedy2015} confirmed these results but recommended caution when applying social behaviours in a tutoring context. 
@@
 
-%We also wanted to study the influence of being in a group or alone when interacting with the robot.
-%At the difference from the group configuration, in the group configuration, other children were witnessing the interaction with the child.
-
 \section{METHOD}
 The experiment took place in a primary school in Switzerland where children are taught in English.
-In this experiment, we targeted children aged 5 who start handwriting at that age, but do not typically master it yet.
-The children interacted with the robot under two conditions of the F-Formation in a random order.
+In this experiment, we targeted children aged 5 y.o. who start handwriting, but do not typically master it yet.
+The children interacted with the robot under two conditions of the F-Formation in a counterbalanced manner.
 
@@
 when teaching it in a side-by-side configuration for several reasons.
-The side-by-side arrangement corresponds to a peer teaching arrangement, unlike the face-to-face teaching arrangement, which is more frequent seen in a teacher-student relationship.
-Also, in the side-by-side formation, the robot and the child have the same perspective of the shared tablet on which they write.
+The side-by-side arrangement corresponds to a cooperative arrangement which is close to a peer teaching setting, unlike the face-to-face teaching arrangement, which is more frequent seen in competitive or conversation tasks (closer to a teacher-student relationship).
+Also, in the side-by-side formation, the robot and the child have the same visual perspective of the shared tablet on which they write.
 Perspective sharing is an ability that facilitates mutual understanding \cite{berlin2006perspective}.
-Hence by having the robot and the child side-by-side, the mutual understanding would be eased.
+Hence by having the robot and the child side-by-side, higher mutual understanding would be expected.
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{./figures/f2f_photot.png}
+  \includegraphics[width=0.7\linewidth]{./figures/f2f_photot.png}
   \caption{Face to face spatial formation}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{./figures/s2s_photo2t.jpg}
+  \includegraphics[width=0.7\linewidth]{./figures/s2s_photo2t.jpg}
   \caption{Side by Side spatial formation}
@@
 \end{figure*}
+
 Apart from this change in the spatial setting, the interaction was kept the same. 
@@
 As the robot would start to write this word. It was set to be a very bad writer at the beginning of the first session for each child.
-The child could then give a feedback to the robot by pressing thumbs up or a thumbs down buttons how many time they wanted.
+The child could then give a feedback to the robot by pressing thumbs up or a thumbs down buttons how many times they wanted.
 The child would then use a pen and demonstrate how to write the word and the robot would then rewrite the word using the demonstration of the child.
@@
 Indeed, in our learning by teaching activity, the robot has also a hidden pedagological role. It's progress aim actually to make the child practice and think about his/her own way of writing. 
-In that sens, we can set attentional targets as proposed by \cite{sharma2014me} when the \emph{with-me-ness} was first introduced for Computer Supported Collaborative Learning.
+In that sense, we can set attentional targets as proposed by \cite{sharma2014me} when the \emph{with-me-ness} was first introduced for Computer Supported Collaborative Learning.
 
@@
 The with-me-ness is initially set to 0.5 and takes values from 0 to 1.
-According to the state in which the activity is, (robot is writing, child is writing,\dots) the with-me-ness will be increased if the child looks at a target that is in the set of targets that are optimum within this particular state of the activity.
+According to the state in which the activity is, (robot is writing, child is writing,\dots) the with-me-ness will be increased if the child looks at a target that is in the set of task-related targets (expected within this particular state of the activity).
 We record these targets and the with-me-ness at a frequency of about $1Hz$.
-The evolution of the withmeness is computationaly attenuated in order to remove noisy data and we set a weight on the update at 10\% (90\% is the previous state).
+The evolution of the withmeness is computationaly attenuated in order to remove noisy data (by using the weighted cumulative of the withmeness value).
 
-The targets are defined according to their spatial relation with the camera used (placed on the table at the robot's feet).
+The targets were defined according to their spatial relation with the camera used (placed on the table at the robot's feet).
 The position of the targets was changed according to the F-formation condition, but the camera stayed at the same position
@@
 
-%todo boucle avec Hypo
-
 \subsection{Reward Mechanism}
-The tablet interface on which the child and the robot practice their handwriting also contains two buttons that allow the child to give a positive (green thumb-up) or negative (red thumb-down) feedback to the robot's handwriting.
+The tablet interface on which the child and the robot practice their handwriting shows two buttons that allow the child to give a positive (green thumb-up) or negative (red thumb-down) feedback to the robot's handwriting.
 After every trial of the robot, the child could click on these feedback buttons as much as he/she wants.
@@
 Since the learning algorithm took as input the child's demonstration, if the child provided repeatedly the exact same demonstration, then the robot would converge faster to his/her handwriting.
-This score is hence a hint on children's regularity, with the underlying assumption that the regularity handwriting is a sign of progress.
-Since children are teaching the robot, they may judge the robot's handwriting according to their provided demonstration, and compare simply their demonstration with the robot's.
+This score is hence a hint on children's regularity, with the underlying assumption that the regularity in handwriting is a sign of legibility.
+%Since children are teaching the robot, they may judge the robot's handwriting according to their provided demonstration, and compare simply their demonstration with the robot's.
 
@@
 We also computed the evolution of this score at each demonstration.
-We represent the evolution of the robot's handwriting with different states:
+We represented the evolution of the robot's handwriting with different states:
 'S=': the first trial of this word by the robot, 'S-': the score is decreasing and 'S+' the score is increasing. 
-If the child change a lot his/her way of writing between consecutives demonstration, the score would then deacrease.
+If the child was changing a lot his/her way of writing between consecutives demonstration, the score would then deacrease.
 In the contrary, the regularity of the demonstration would make the score increase rapidly.
@@
 %The effect of IV on DV was not statistically significant ($F_{a,b}= C, ns$). 
-In this section, we present results from this study on 12 children that interacted with the robot twice in the two conditions (side-by-side and face-to-face).
-We studied the impact on the F-formation on the reward given with the buttons, the performance and the with-me-ness.
+%In this section, we present results from this study on 12 children that interacted with the robot twice in the two conditions (side-by-side and face-to-face).
+%We studied the impact on the F-formation on the reward given with the buttons, the performance and the with-me-ness.
 
 \subsection{Reward Mechanism}
+Children gave feedback with an average of 3 feedbacks per demonstration.
+Figure \ref{fig:uf_nb} shows the average evolution along the demonstrations of the sum of feedbacks given for all children and for both spatial condition.
+We noticed that the feedback is first negative and grows towards a positive feedback after each demonstration.
+In average for all the children, the sum of feedbacks stayed negative until the 5th demonstration.
 Children well understood that they were teaching the robot and often gave bad scores for the first untrained trial of the robot.
-Children gave feedback with an average of 3 feedbacks per demonstration.
-Figure \ref{fig:uf_nb} shows the average evolution along the demonstrations of the sum of feedbacks given for all children.
-We noticed that the feedback is first negative and grows towards a positive feedback after each demonstration.
 Children usually gave a positive feedback just before changing the word taught to the robot.
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{figures/plots/evoldemo}
+	\includegraphics[width=0.75\linewidth]{figures/plots/evoldemocondbis}
 	\caption{Evolution of Feedback along the demonstration index}
@@
 \end{figure}
-
-The effect of the F-Formation on the feedback from the child was statistically significant ( $F_{1,272}= 4.396, p<0.05$).
+Eventhough the average feedback was incrasing along with the number of demonstration for both condition, they don't seems to increase the same way(see Figure\ref{fig:uf_nb})
+The effect of the F-Formation on the feedback from the child was statistically significant (Anova Reapted mesures within subjects: $F_{1,272}= 4.396, p<0.05$).
 As, illustrated on Figure \ref{fig:userfeedback_fformation_se}, the average feedback per demonstration was greater($M=0.03, SD=1, N=147$) for the side-by-side condition compare to the face-to-face condition ($M=-0.23, SD=0.98, N=138$).
@@
  	\centering
- 	\includegraphics[width=0.6\linewidth]{figures/plots/userfeedback_fformation_se}
+ 	\includegraphics[width=0.58\linewidth]{figures/plots/userfeedback_fformation_se}
  	\caption{Feedback According to the F-Formation}
@@
 We also observe an order effect showing that children tended to give higher feedback in the second session compare to the first one.
-%todo see if add significance here 
+%todo see if adding test
 This can simply be explained by the fact that the robot's learning state was progressive between the two session. 
@@
 \subsection{With-me-ness}
-Generally, children understood the dynamics of the interaction, as in general the with-me-ness stayed above 0.5 throughout the interaction (started et 0.5 but always finished above).
+Children understood the dynamics of the interaction, as in general the with-me-ness stayed above 0.5 throughout the interaction (started et 0.5 but always finished above).
 \begin{figure}	
@@
 \end{figure}
- The effect of the F-Formation on the with-me-ness of the child was statistically significant ( $F_{1,15983}= 293.2, p<0.001$).
+ The effect of the F-Formation on the with-me-ness of the child was statistically significant (Anova Reapted mesures within subjects: $F_{1,15983}= 293.2, p<0.001$).
 The with-me-ness was greater($M=0.79, SD=0.18, N=7722$) for the face-to-face condition compare to the side-by-side condition ($M=-0.72, SD=0.21, N=8267$) (see Figure \ref{fig:withmeness_fformation_ci}).
@@
 
-Again, we observed an order effect with the withmeness increasing between the two session. 
-As children were more confordable with the system, it is logic that they started to learn the dynamics of the interaction knwoing when to look at the selection tablet, the writing tablet and the robot.
+Again, we observed an order effect with the withmeness increasing between the two sessions. 
+As children were more confordable with the system, it is logic that they started to learn the dynamics of the interaction knowing when to look at the selection tablet, the writing tablet and the robot.
 %todo add stats
@@
 There was no significant difference between the conditions.
+% ($F(1,11)=0, p=0.986$).
 
@@
 No significant difference in the writing time was found.
+%($F(1,11)=1.507, p=0.24$).
 
@@
 \subsubsection{Writing Score for the Robot}
-There was no significant difference of score in the F-formation condition tested (side-by-side:$M=0.80, SD=0.08, N=135$, face-to-face: $M=0.79, SD=0.08, N=191$).
+There was no significant difference of writing score in the F-formation condition tested (side-by-side:$M=0.80, SD=0.08, N=135$, face-to-face: $M=0.79, SD=0.08, N=191$, Anova Reapted mesures within subjects:$p>0.1$).
 This result means that the children were teaching as well in the face-to-face condition as in the side-by-side condition.
 However, results showed significant differences in terms of feedback given to the robot regarding the score of the robot.
+
+We analysed the probabilities of succeding events considering feedback events and score evolution events.
+
 Table~\ref{proba} shows the probabilities of transition from after the score increases and after the score decreases.
-When the score increases, we see that in the face-to-face condition, the probability of positive feedback is smaller than in the side-by side condition.
-On the contrary, the probability of having a negative feedback after the score having decreased is higher in the face-to-face condition.
-We can also notice that when the score decreases, the probability of having a positive feedback is twice higher in the side-by-side condition
+We notice that in general the positive feedback probalities are higher for the side-by-side condition in comparison to the face-to-face. 
+On the contrary, the probability of having a negative feedback after is higher in the face-to-face condition.
+We can also notice that when the score decreases, the probability of having a positive feedback is almost twice higher in the side-by-side condition (total number of events $= $).
 
@@
 \midrule
-Score Increases & 	0.16 / \emph{0.27}	& 0.46 / \emph{0.47} \\
-Score Decreases &	0.15 / \emph{0.32}	& 0.42 / \emph{0.28} \\
+Score Increases & 	0.37 / \emph{0.44}	& 0.38 / \emph{0.27} \\
+Score Decreases &	0.27 / \emph{0.46}	& 0.36 / \emph{0.20} \\
 \bottomrule
@@
 \end{table}
+
 \begin{figure*}
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{./figures/faceface_score}
+		\includegraphics[width=0.8\linewidth]{./figures/states/states_f2f}
 		\caption{Face to face spatial formation}
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{./figures/sidebiside_score}
+		\includegraphics[width=0.8\linewidth]{./figures/states/statess_sbs}
 		\caption{Side by Side spatial formation}
@@
 Children even rewarded retrogression more often in the side-by-side condition.
+These differences in the transition matrix were not significant (Pearson's Chi-squared test, $X-squared = 30, df = 25, p-value = 0.2243$) and a study with a larger number of participants might have given more precise results.
 
@@
 
-We noticed that the children were expecting the robot to react to the feedback.
+While running the experiments, we noticed that the children were expecting the robot to react to the feedback, and the robot was moving only when writing. 
 We are working on different form of reactions for future experiments to allow the robot to react according to the feedback from the child and also in perspective with the fairness of the feedback regarding the score of the robot.
 For instance, if the child gives a positive feedback when the robot is actually improving, the robot should display a positive emotion.
-If it is given a positive feedback but does not actually make any progress, he might express doubt to force the child to be more exigent.
+If it is given a positive feedback but does not actually make any progress, it might express doubt to force the child to be more exigent.
 
-Some limitations are however to be noticed. 
-In this experiment, the robot was moving only when writing. 
-Even if our results showed that the side-by-side elicited more positive feedback from the children, in the case where the robot would display some emotional reaction during the interaction, the same effect might not be observed.
-We plan to enhance the interaction with such reaction and to research the effect of such reactions on the child's perception of the robot's progresses. 
+Even if our results showed that the side-by-side elicited more positive feedback from the children, statistical significance was not reached, and if the robot would display some emotional reaction during the interaction, the same effect might not be observed.
+We plan to enhance the interaction with some behavioural reaction and to research the effect of such reactions on the child's perception of the robot's progresses. 
 Long term studies might also bring more insights to theses results in order to see if the effect of the spatial arrangement sustain over time.
+
+To conclude, we believe that spatial arragement can be used as a non-verbal cue of communication to contextualise the interaction (as cooperative or competitive for instance).
 %discuss results regarding the literature, same ? different arguments for/against initial premise, limitations, etc.

### 2016-05-24 paper-Ro_Man-2016.tex
fix accents

@@
 
-\author{Wafa Johal$^{1}$, Alexis Jacq$^{1}$$^{2}$, Ana Paiva$^{2}$ and Pierre Dillenbourg$^{1}$  % <-this % stops a space
+\author{Wafa Johal$^{1}$$^{2}$, Alexis Jacq$^{1}$$^{3}$, Ana Paiva$^{3}$ and Pierre Dillenbourg$^{1}$  % <-this % stops a space
 \thanks{}% <-this % stops a space
 \thanks{$^{1}$ CHILI Lab,
-        École Fédérale Polytechnique Lausanne, Switzerland
+	$^{2}$ LSRO Lab,
+        \'{E}cole F\'{e}d\'{e}rale Polytechnique Lausanne, Switzerland
         {\tt\small firstname.lastname@epfl.ch}}%
-\thanks{$^{2}$Instituto Superior T\'{e}cnico, University of Lisbon, Portugal
+\thanks{$^{3}$Instituto Superior T\'{e}cnico, University of Lisbon, Portugal
         {\tt\small firstname.lastname@inesc-id.pt}}%
@@
 In this paper, we present an experiment in the context of a child-robot interaction where we study the influence of the child-robot spatial arrangement on the child's focus of attention and the perception of the robot's performance.
-In the ``''Co-Writer learning by teaching'' activity, the child teaches a Nao robot how to handwrite.
+In the ``Co-Writer learning by teaching'' activity, the child teaches a Nao robot how to handwrite.
 Usually only face-to-face spatial arrangements are tested in educational child robot interactions, but we explored two spatial conditions from Kendon's F-formation, the side-by-side and the face-to-face formations in a within subject experiment.

### 2016-05-25 paper-Ro_Man-2016.tex
changes from pierres comments

@@
 %\usepackage[utf8]{inputenc}
-
+\usepackage{slashbox}
+\setlength{\belowcaptionskip}{-8pt}
 \usepackage{tikz}
@@
 %In our research context, we consider the problem of how robots could enhance the effectiveness of education.
-The potential of robots for individual adaptation and their ability to handle repetitive tasks makes them fit well in the educational world.
+The potential of robots for individual adaptation and their physical ability makes them fit well in the educational world.
+%todo on voi si on enleve
+We investigate how robots can bring added value for learning by designing and selecting relevant physical tas and setting up the appropriate interaction.
 In that vein, the Co-Writer projects aims to help children with difficulties in handwriting \cite{hood2015when}.
@@
 Under this paradigm, by teaching a robot (Nao from Aldebaran) how to write, children learn and improve their handwriting at the same time.
-The activity also plays with the \emph{protégé effect}, which makes children more motivated in practising for the robot than for themselves.
+The activity also plays with the \emph{protégé effect}, which makes children more engaged in practising for the robot than for themselves.
 
@@
 Case studies presented in \cite{jacq2016building} showed that children were able to stay engaged in long term interactions with repeated sessions within the Co-Writer activity in real pedagogical/therapeutic contexts.
-These works proved to have a positive effect on the extrinsic motivation of the children when practising their handwriting, thanks to the protégé effect.
+These works proved to have a positive effect on the extrinsic motivation of the children when practicing their handwriting, thanks to the protégé effect.
 
@@
 In home environments, robots will be expected to perform their functions in a manner that is clearly understandable and predictable by the humans around.
-This requires adaptive personalisation of the robot to the individual needs of the humans, but also to the task being currently performed.
+This requires adaptive personalization of the robot to the individual needs of the humans, but also to the task being currently performed.
 Some previous studies showed that the spatial setting with a robot was also a way to convey non-verbal messages and it serves to influence the relationship with the user\cite{Takayama2009,kristoffersson2013measuring}.
@@
 
-In educational child-robot interaction, quite often, the robot is placed as a tutor or a peer helping the child, and uses social capabilities to enhance the learning \cite{Saerbeck2010}.
+In educational child-robot interaction, quite often, the robot is placed in front of the learner playing the role of a tutor or a peer helping the child, and uses social capabilities to enhance the learning \cite{Saerbeck2010}.
 Kanda \cite{Kanda2004} reported an experiment involving children that learns from a robot as they would from a peer.
@@
 \cite{Leyzberg2014} showed in a face-to-face setting that the physical presence of the robot produced measurable learning gains.
-\cite{Kennedy2015} confirmed these results but recommended caution when applying social behaviours in a tutoring context. 
+\cite{Kennedy2015} confirmed these results but recommended caution when applying social behaviors in a tutoring context. 
 %explain why caution
@@
 Our goal was to investigate the effect of spatial arrangement on the interaction.
-We expected that children would give better feedback to the
+We expected that children would give better feedback(see \ref{ss:feedback}) to the robot
 when teaching it in a side-by-side configuration for several reasons.
@@
 Several hypotheses were made concerning the influence of the spatial arrangement on the interaction.
-We expected that the gaze behaviour of the child would vary according to the spatial configuration.
+We expected that the gaze behavior of the child would vary according to the spatial configuration.
 More gazing at the robot's head would be expected in the face-to-face condition.
 Our research question was to measure the degree to which this also influenced the way children behaved as a teacher (were they more or less severe with the robot facing them).
-As children give a feedback to the robot for each demonstratation, we intend to measure if there is any difference between vis-a-vis and side-by-side regarding this feedback (does the side-by-side condition trigger more positive feedback?).
+As children give a feedback to the robot for each demonstration, we intend to measure if there is any difference between vis-a-vis and side-by-side regarding this feedback (does the side-by-side condition trigger more positive feedback?
+or more appropriate feedback?).
 %Because of this influence of facing the robot and being able to see its head, we also believed that the robot would be perceived as more competent in the face to face condition and hence collect more positive feedback from the child.
@@
 
-The engagement of the child in the task can also be influenced by the arrangement.
+The degree of  engagement of the child in the task can also be influenced by the arrangement.
 For that particular aspect, we will measure the number of repetitions of each word, as well as the with-me-ness, which is discussed in the following section.
@@
 In a simple way, the \emph{with-me-ness} value will increase if the child looks at the specific set of targets, or else it decreases.
-This measure allows us to see if the child is engaged in the interaction and is looking at the tablet or the robot's head when he/she should.
-Indeed, in our learning by teaching activity, the robot has also a hidden pedagological role. It's progress aim actually to make the child practice and think about his/her own way of writing. 
-In that sense, we can set attentional targets as proposed by \cite{sharma2014me} when the \emph{with-me-ness} was first introduced for Computer Supported Collaborative Learning.
+This measure allows us to see if the child is engaged in the interaction and is looking at the tablet or the robot's head when he/she is expected to (according to the task).
+Indeed, in our learning by teaching activity, the robot has also a hidden pedagogical role. It's progress aim actually to make the child practice and think about his/her own way of writing. 
+In that sense, we can set attentional targets as proposed by \cite{sharma2014me} when the \emph{with-me-ness} was first introduced to measure learner's attention to teachers in MOOC videos.
 
@@
 We record these targets and the with-me-ness at a frequency of about $1Hz$.
-The evolution of the withmeness is computationaly attenuated in order to remove noisy data (by using the weighted cumulative of the withmeness value).
+The evolution of the withmeness is computationally attenuated in order to remove noisy data (by using the weighted cumulative of the withmeness value).
 
@@
 
+\vspace{-0.1cm}
 \subsection{Reward Mechanism}
+\vspace{-0.2cm}
+\label{ss:feedback}
 The tablet interface on which the child and the robot practice their handwriting shows two buttons that allow the child to give a positive (green thumb-up) or negative (red thumb-down) feedback to the robot's handwriting.
@@
 'S=': the first trial of this word by the robot, 'S-': the score is decreasing and 'S+' the score is increasing. 
-If the child was changing a lot his/her way of writing between consecutives demonstration, the score would then deacrease.
+If the child was changing a lot his/her way of writing between consecutives demonstration, the score would then decreasee.
 In the contrary, the regularity of the demonstration would make the score increase rapidly.
@@
 \subsection{Reward Mechanism}
-Children gave feedback with an average of 3 feedbacks per demonstration.
+\vspace{-0.2cm}
+Children gave feedback with an average of 3 feedbacks per demonstration (i.e. per interaction loop).
+We summed the feedbacks for each demo with positive feedback counted as $+1$ and negative as $-1$.
 Figure \ref{fig:uf_nb} shows the average evolution along the demonstrations of the sum of feedbacks given for all children and for both spatial condition.
@@
 	\includegraphics[width=0.75\linewidth]{figures/plots/evoldemocondbis}
-	\caption{Evolution of Feedback along the demonstration index}
+	\caption{Evolution of Feedback along the demonstration index(Mean: line , SD: filled area)}
 	\label{fig:uf_nb}
 \end{figure}
-Eventhough the average feedback was incrasing along with the number of demonstration for both condition, they don't seems to increase the same way(see Figure\ref{fig:uf_nb})
-The effect of the F-Formation on the feedback from the child was statistically significant (Anova Reapted mesures within subjects: $F_{1,272}= 4.396, p<0.05$).
+Even though the average feedback was increasing along with the number of demonstration for both condition, they don't seems to increase the same way(see Figure\ref{fig:uf_nb})
+The effect of the F-Formation on the feedback from the child was statistically significant (Anova Repeated measures within subjects: $F_{1,272}= 4.396, p<0.05$).
 As, illustrated on Figure \ref{fig:userfeedback_fformation_se}, the average feedback per demonstration was greater($M=0.03, SD=1, N=147$) for the side-by-side condition compare to the face-to-face condition ($M=-0.23, SD=0.98, N=138$).
@@
  	\includegraphics[width=0.58\linewidth]{figures/plots/userfeedback_fformation_se}
- 	\caption{Feedback According to the F-Formation}
+ 	\caption{Feedback Sum According to the F-Formation (Means and Confidence Intervals)}
  	\label{fig:userfeedback_fformation_se}
@@
 \subsection{With-me-ness}
+\vspace{-0.2cm}
 Children understood the dynamics of the interaction, as in general the with-me-ness stayed above 0.5 throughout the interaction (started et 0.5 but always finished above).
@@
 \label{fig:withmeness_fformation_ci}
+
 \end{figure}
- The effect of the F-Formation on the with-me-ness of the child was statistically significant (Anova Reapted mesures within subjects: $F_{1,15983}= 293.2, p<0.001$).
+ The effect of the F-Formation on the with-me-ness of the child was statistically significant (Anova Repeated measures within subjects: $F_{1,15983}= 293.2, p<0.001$).
 The with-me-ness was greater($M=0.79, SD=0.18, N=7722$) for the face-to-face condition compare to the side-by-side condition ($M=-0.72, SD=0.21, N=8267$) (see Figure \ref{fig:withmeness_fformation_ci}).
@@
 
-The centrer graph of Figure \ref{fig:times} shows the average response time for the demonstration provided by the children for the two spatial arrangement conditions.
+The center graph of Figure \ref{fig:times} shows the average response time for the demonstration provided by the children for the two spatial arrangement conditions.
 The response time is the delay between the time when the robot finishes to write and the time when the child touches the tablet.
@@
 \subsubsection{Writing Score for the Robot}
-There was no significant difference of writing score in the F-formation condition tested (side-by-side:$M=0.80, SD=0.08, N=135$, face-to-face: $M=0.79, SD=0.08, N=191$, Anova Reapted mesures within subjects:$p>0.1$).
+There was no significant difference of writing score in the F-formation condition tested (side-by-side:$M=0.80, SD=0.08, N=135$, face-to-face: $M=0.79, SD=0.08, N=191$, Anova Repeated measures within subjects:$p>0.1$).
 This result means that the children were teaching as well in the face-to-face condition as in the side-by-side condition.
@@
 
-We analysed the probabilities of succeding events considering feedback events and score evolution events.
+We analyzed the probabilities of succeeding events considering feedback events and score evolution events.
 
 Table~\ref{proba} shows the probabilities of transition from after the score increases and after the score decreases.
-We notice that in general the positive feedback probalities are higher for the side-by-side condition in comparison to the face-to-face. 
+We notice that in general the positive feedback probabilities are higher for the side-by-side condition in comparison to the face-to-face. 
 On the contrary, the probability of having a negative feedback after is higher in the face-to-face condition.
@@
 \centering
-\caption{\small Probability of feeback given the score per word in  the two conditions : face-to-face / \emph{side-by-side}}
+\caption{\small Probability of feedback given the score per word in  the two conditions : face-to-face / \emph{side-by-side}}
 \label{proba}
-\begin{tabular}{l|p{2cm}|p{2cm}l@{}}
+\begin{tabular}{l|p{1.3cm}|p{1.3cm}|p{1.2cm}}
 \toprule
-Score event & Positive Feedback & Negative Feedback \\
+\backslashbox{Score Event}{Feedback} & Positive  & Negative & None \\
 \midrule
-Score Increases & 	0.37 / \emph{0.44}	& 0.38 / \emph{0.27} \\
-Score Decreases &	0.27 / \emph{0.46}	& 0.36 / \emph{0.20} \\
+Score Increases & 	0.37 / \emph{0.44}	& 0.39 / \emph{0.27} & 0.24 / \emph{0.29} \\
+Score Decreases &	0.28 / \emph{0.47}	& 0.36 / \emph{0.20} & 0.36 / \emph{0.33} \\
 \bottomrule
@@
 
-All the transitions between the scores and the feedback buttons are illustrated on Figure \ref{fig:state}
-Children were displaying a more positive attitude towards the robot when placed in side-by-side position.
-This positive attitude was showed by rewarding more improvements of the robot and also penalising less the retrogression of the robot's writing.
+All the transitions between the scores and the feedback buttons are illustrated on Figure \ref{fig:state}.
+Children were displaying a more positive attitude towards the robot when placed in side-by-side position even when the robot was not improving.
+This positive attitude was showed by rewarding more improvements of the robot and also penalizing less the retrogression of the robot's writing.
 Children even rewarded retrogression more often in the side-by-side condition.
+The reward given by children showed to be not often appropriate. 
+For instance in the face-to-face condition, score increasing got more than a third of the time given a negative feedback.
 These differences in the transition matrix were not significant (Pearson's Chi-squared test, $X-squared = 30, df = 25, p-value = 0.2243$) and a study with a larger number of participants might have given more precise results.
@@
 \section{DISCUSSIONS AND CONCLUSIONS}
+\vspace{-0.1cm}
 In this paper we presented a study that aimed to elicit the effect of spatial arrangement on a learning task between a robot and a child.
@@
 Even if our results showed that the side-by-side elicited more positive feedback from the children, statistical significance was not reached, and if the robot would display some emotional reaction during the interaction, the same effect might not be observed.
-We plan to enhance the interaction with some behavioural reaction and to research the effect of such reactions on the child's perception of the robot's progresses. 
+We plan to enhance the interaction with some behavioral reaction and to research the effect of such reactions on the child's perception of the robot's progresses. 
 Long term studies might also bring more insights to theses results in order to see if the effect of the spatial arrangement sustain over time.
 
-To conclude, we believe that spatial arragement can be used as a non-verbal cue of communication to contextualise the interaction (as cooperative or competitive for instance).
+To conclude, we believe that spatial arrangement can be used as a non-verbal cue of communication to contextualize the interaction (as cooperative or competitive for instance).
 %discuss results regarding the literature, same ? different arguments for/against initial premise, limitations, etc.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\vspace{-0.1cm}
 \section*{ACKNOWLEDGMENT}
+\vspace{-0.2cm}
+\small
 This research was partially supported by the Funda\c{c}\~{a}o para a Ci\^{e}ncia

### 2016-05-25 paper-Ro_Man-2016.tex
fix figue evol feedback
some typos

@@
 	$^{2}$ LSRO Lab,
-        \'{E}cole F\'{e}d\'{e}rale Polytechnique Lausanne, Switzerland
+        \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Switzerland
         {\tt\small firstname.lastname@epfl.ch}}%
-\thanks{$^{3}$Instituto Superior T\'{e}cnico, University of Lisbon, Portugal
+\thanks{$^{3}$Instituto Superior T\'{e}cnico (IST), University of Lisbon, Portugal
         {\tt\small firstname.lastname@inesc-id.pt}}%
@@
 Usually only face-to-face spatial arrangements are tested in educational child robot interactions, but we explored two spatial conditions from Kendon's F-formation, the side-by-side and the face-to-face formations in a within subject experiment.
-We estimated the gaze behaviour of the child and their consistency in grading the robot with regard to the robot's progress in writing. 
+We estimated the gaze behavior of the child and their consistency in grading the robot with regard to the robot's progress in writing. 
 Even-though the demonstrations provided by children were not different between the two conditions (i.e.
@@
 	\includegraphics[width=0.75\linewidth]{figures/plots/evoldemocondbis}
-	\caption{Evolution of Feedback along the demonstration index(Mean: line , SD: filled area)}
+	\caption{Evolution of Feedback along the demonstration index(Mean: line , Confidence Interval 0.95: filled area)}
 	\label{fig:uf_nb}

### 2016-05-27 paper-Ro_Man-2016.tex
changes from reviewers requests

@@
 \usepackage{slashbox}
-\setlength{\belowcaptionskip}{-8pt}
+\setlength{\belowcaptionskip}{-11pt}
 \usepackage{tikz}
@@
 
-\author{Wafa Johal$^{1}$$^{2}$, Alexis Jacq$^{1}$$^{3}$, Ana Paiva$^{3}$ and Pierre Dillenbourg$^{1}$  % <-this % stops a space
+\author{Wafa Johal$^{1,}$$^{2}$, Alexis Jacq$^{1,}$$^{3}$, Ana Paiva$^{3}$ and Pierre Dillenbourg$^{1}$  % <-this % stops a space
 \thanks{}% <-this % stops a space
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{./figures/f2f_photot.png}
+  \includegraphics[width=0.7\linewidth]{./figures/f2f_photott.jpg}
   \caption{Face to face spatial formation}
@@
 We record these targets and the with-me-ness at a frequency of about $1Hz$.
-The evolution of the withmeness is computationally attenuated in order to remove noisy data (by using the weighted cumulative of the withmeness value).
+The evolution of the with-me-ness is computationally attenuated in order to remove noisy data (by using the weighted cumulative of the with-me-ness value).
 
@@
 
-Again, we observed an order effect with the withmeness increasing between the two sessions. 
-As children were more confordable with the system, it is logic that they started to learn the dynamics of the interaction knowing when to look at the selection tablet, the writing tablet and the robot.
+Again, we observed an order effect with the with-me-ness increasing between the two sessions. 
+As children were more comfortable with the system, it is logic that they started to learn the dynamics of the interaction knowing when to look at the selection tablet, the writing tablet and the robot.
 %todo add stats
@@
 %Residuals 15985  602.0   0.038        
-
+\begin{figure*}[ht]
+	\centering
+	\includegraphics[width=0.25\linewidth]{figures/plots/repetition_fformation_ci}
+	\includegraphics[width=0.25\linewidth]{figures/plots/responseTime_fformation_ci}
+	\includegraphics[width=0.25\linewidth]{figures/plots/writingTime_fformation_ci2}
+	\caption{Number of demonstration per word (left), response time (center), writing time (right) - (Means and Confidence Intervals)}
+	\label{fig:times}
+\end{figure*}
 \subsection{Performances}
@@
 
-\begin{figure*}[ht]
-	\centering
-	\includegraphics[width=0.25\linewidth]{figures/plots/repetition_fformation_ci}
-	\includegraphics[width=0.25\linewidth]{figures/plots/responseTime_fformation_ci}
-	\includegraphics[width=0.25\linewidth]{figures/plots/writingTime_fformation_ci2}
-	\caption{Number of demonstration per word (left), response time (center), writing time (right) - (Means and Confidence Intervals)}
-	\label{fig:times}
-	\end{figure*}
-
 These results show that children when not spending more time per word in one condition of the other. 
@@
 %These results confirm the fact that the robot is better suited here for individual interaction.
-\subsubsection{Writing Score for the Robot}
-There was no significant difference of writing score in the F-formation condition tested (side-by-side:$M=0.80, SD=0.08, N=135$, face-to-face: $M=0.79, SD=0.08, N=191$, Anova Repeated measures within subjects:$p>0.1$).
-This result means that the children were teaching as well in the face-to-face condition as in the side-by-side condition.
-However, results showed significant differences in terms of feedback given to the robot regarding the score of the robot.
-
-We analyzed the probabilities of succeeding events considering feedback events and score evolution events.
-
-Table~\ref{proba} shows the probabilities of transition from after the score increases and after the score decreases.
-We notice that in general the positive feedback probabilities are higher for the side-by-side condition in comparison to the face-to-face. 
-On the contrary, the probability of having a negative feedback after is higher in the face-to-face condition.
-We can also notice that when the score decreases, the probability of having a positive feedback is almost twice higher in the side-by-side condition (total number of events $= $).
-
-\begin{table}[ht!]
-\centering
-\caption{\small Probability of feedback given the score per word in  the two conditions : face-to-face / \emph{side-by-side}}
-\label{proba}
-\begin{tabular}{l|p{1.3cm}|p{1.3cm}|p{1.2cm}}
-\toprule
-\backslashbox{Score Event}{Feedback} & Positive  & Negative & None \\
-\midrule
-Score Increases & 	0.37 / \emph{0.44}	& 0.39 / \emph{0.27} & 0.24 / \emph{0.29} \\
-Score Decreases &	0.28 / \emph{0.47}	& 0.36 / \emph{0.20} & 0.36 / \emph{0.33} \\
-\bottomrule
-\end{tabular}
-\end{table}
 
@@
 \end{figure*}
+
+\subsubsection{Writing Score for the Robot}
+There was no significant difference of writing score in the F-formation condition tested (side-by-side:$M=0.80, SD=0.08, N=135$, face-to-face: $M=0.79, SD=0.08, N=191$, Anova Repeated measures within subjects:$p>0.1$).
+This result means that the children were teaching as well in the face-to-face condition as in the side-by-side condition.
+However, results showed significant differences in terms of feedback given to the robot regarding the score of the robot.
+
+We analyzed the probabilities of succeeding events considering feedback events and score evolution events.
+
+\begin{table}[ht!]
+	\centering
+	\caption{\small Probability of feedback given the score per word in  the two conditions : face-to-face / \emph{side-by-side}}
+	\label{proba}
+	\begin{tabular}{l|p{1.3cm}|p{1.3cm}|p{1.2cm}}
+		\toprule
+		\backslashbox{Score Event}{Feedback} & Positive  & Negative & None \\
+		\midrule
+		Score Increases & 	0.37 / \emph{0.44}	& 0.39 / \emph{0.27} & 0.24 / \emph{0.29} \\
+		Score Decreases &	0.28 / \emph{0.47}	& 0.36 / \emph{0.20} & 0.36 / \emph{0.33} \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+Table~\ref{proba} shows the probabilities of transition of feedback events (positive or negative) after the score increases or after the score decreases (computed using Markov Chain).
+We notice that in general the positive feedback probabilities are higher for the side-by-side condition in comparison to the face-to-face. 
+On the contrary, the probability of having a negative feedback after is higher in the face-to-face condition.
+We can also notice that when the score decreases, the probability of having a positive feedback is almost twice higher in the side-by-side condition (total number of events $= $).
 
@@
 To conclude, we believe that spatial arrangement can be used as a non-verbal cue of communication to contextualize the interaction (as cooperative or competitive for instance).
+We also believe that choices in terms of spatial arrangements in HRI studies should be thoroughly made as they may influence the interaction.
 %discuss results regarding the literature, same ? different arguments for/against initial premise, limitations, etc.
@@
 \small
-\bibliographystyle{abbrv}
+\bibliographystyle{ieeetr}
 \bibliography{fformation_cowriter}
